---
title: "Workshop 6"
output: html_document
date: "2023-07-19"
---

```{r setup, include=FALSE} 
knitr::opts_chunk$set(warning = FALSE, message = FALSE) 
```

# Create R Project

1. Open RStudio
2. In the top right hand corner, click the R cube and select "New Project"
3. Choose "New Directory" and "New Project"
4. Enter a name for your new project 
5. Browse the location for where you want your project to be saved
6. Click "Create Project"

# Load libraries

```{r}
library(tidyverse)
library(janitor)
library(ggeasy)
library(knitr)
```




# Research Questions

[Women's World Cup Data](https://www.kaggle.com/datasets/mattop/fifa-womens-world-cup-stats?resource=download)

1. Which 10 countries have the most goals? 
2. How has the average age of women playing in the world cup changed over the years?

# Read in data 

When I read in my data, I always start by looking at the variable names (do the names make sense? are they easy to read? are they consistent?)
  - `janitor::clean_names()` is my go to for automatically cleaning the variable names
  
```{r}
X <- read.csv('womens-world-cup.csv')
Xt <- read_csv('womens-world-cup.csv')  # note the underscore. Today I learned!

wc_data_raw <- read_csv('womens-world-cup.csv') %>% 
  clean_names()

abcdefghi_abcdefghi_abcdefghi_abcdefghi_abcdefghi_abcdefghi_abcdefghi_abcdefghi_abcdefghi_abcdefghij <- 10  # hey look a 100-char var name works fine.


```




# Research Question 1: Which 10 countries have the most goals? 

## Clean and organize data

- Next, I think about my research question and decide which variables do I need 
- And then continue organizing the data to answer my research question

```{r}
wc_data_raw %>%
  select(squad, year, age, matches_played, goals) %>% 
  group_by(squad) %>% 
  summarise(total_goals = sum(goals)) %>% 
  arrange(desc(total_goals)) %>% 
  head(10) -> wc_goals_top10

wc_goals_top10 %>% 
  kable()

```

## How about the highest peak?

What countries have the top number of goals in a year?

```{r highest-max}
wc_data_raw %>%
  group_by(squad) %>% 
  summarise(max_goals = max(goals)) %>% 
  arrange(desc(max_goals)) %>% 
  head(10) %>% 
  kable()
```

```{r max-squad-and-year}
wc_data_raw %>%
  group_by(squad, year) %>% 
  summarise(max_goals = max(goals)) %>% 
  arrange(desc(max_goals)) %>% 
  head(10) %>% 
  kable()
```

```{r plot1}
wc_data_raw %>%
  group_by(squad) %>% 
  summarise(total_goals = sum(goals)) -> wc_goals

ggplot(wc_goals, aes(squad, total_goals)) +
  geom_col()


```






# August 2 session

## Visualize our results

- Introducing `ggplot`!
- Think about your data, what type of plot would make the most sense?

```{r plot-aug2}

ggplot(wc_goals_top10, aes(
    x = fct_reorder(squad, total_goals),
    total_goals,
    label=total_goals
  )) +
  geom_col() +
  labs(x='Squad', y='Total goals') +
  theme_classic() +   # neat one
  coord_flip() +
  geom_label()

# We did ggeasy too, but I didn't use any.

```



## GGEasy




# Research Question 2: How has the average age of women playing in the world cup changed over the years?

```{r}
wc_data_raw %>%
  mutate(sum_ages = players * age) %>%
  select(year, players, age, sum_ages) %>%
  group_by(year) %>%
  summarise(players_tot = sum(players), sum_ages_tot = sum(sum_ages)) %>%
  mutate(avg_age = sum_ages_tot / players_tot) -> avg_age

avg_age %>% kable()

```

## Visualize our results

```{r}

ggplot(avg_age, aes(x = year, y = avg_age)) +
  geom_point() +
  geom_line()
```

