---
title: "Workshop 6"
output: html_document
date: "2023-07-19"
---

```{r setup, include=FALSE} 
knitr::opts_chunk$set(warning = FALSE, message = FALSE) 
```

# Create R Project

1. Open RStudio
2. In the top right hand corner, click the R cube and select "New Project"
3. Choose "New Directory" and "New Project"
4. Enter a name for your new project 
5. Browse the location for where you want your project to be saved
6. Click "Create Project"

# Load libraries

```{r}
library(tidyverse)
library(janitor)
library(ggeasy)
```

# Research Questions

[Women's World Cup Data](https://www.kaggle.com/datasets/mattop/fifa-womens-world-cup-stats?resource=download)

1. Which 10 countries have the most goals? 
2. How has the average age of women playing in the world cup changed over the years?

# Read in data 

When I read in my data, I always start by looking at the variable names (do the names make sense? are they easy to read? are they consistent?)
  - `janitor::clean_names()` is my go to for automatically cleaning the variable names
  
```{r}


```

# Research Question 1: Which 10 countries have the most goals? 

## Clean and organize data

- Next, I think about my research question and decide which variables do I need 
- And then continue organizing the data to answer my research question

```{r}


```

## Visualize our results

- Introducing `ggplot`!
- Think about your data, what type of plot would make the most sense?

```{r}


```

# Research Question 2: How has the average age of women playing in the world cup changed over the years?

```{r}


```

## Visualize our results

```{r}


```

